---
title: "Exercise 3 - Knitr chunk options"
output: html_document
---

For each knitr code chunk option below

1. Add the option to the code chunk it accompanies.
2. Rerender the file to see what the option does. If you cannot tell, rerender the file both with and without the code chunk.
3. Describe in your own words what the option does.

***

### eval

```{r eval=FALSE}
colMeans(cars)
1 + 1
```
Description:

***

### results

```{r results = 'hide'}
carmeans <- colMeans(cars)
1 + 1
```

```{r}
# Hint: this code would return FALSE if you 
# had used eval = FALSE instead of results='hide' 
# in the chunk above
exists("carmeans")
```
Description:

***

###  echo

```{r echo = FALSE}
plot(cars)
```
Description:

***

### fig.width and fig.height

When adding multiple arguments to a code chunk, separate the arguments by a comma.

```{r fig.width = 5, fig.height = 4}
plot(cars)
```
Description:

***

### message   

```{r message = FALSE}
# packages like to print messages when they load
library(forecast)
```
Description:

***

### warning

```{r warning = FALSE}
warning("This function returns a warning!")
```
Description:

***