---
title: "What's in a name?"
author: "Your name"
date: "Today's date"
output: html_document
---

The code below makes a dygraph from an object named all that has the names "ldeaths", "p.lwr", "p.fit", "p.upr". 

Instead of making `plot(all)` in your report below, you'd like to make a dygraph from your object named all that has the names "x", "lower", "fitted", "upper"

Can you do it? Replace `plot(all)` below with your dygraph code.

```{r}
# loads dygraph library
library(dygraphs)

# preprocesses data (ignore this part:
# we've already preprocessed our data in the report below)
hw <- HoltWinters(ldeaths)
p <- predict(hw, n.ahead = 36, prediction.interval = TRUE)
all <- cbind(ldeaths, p)

# builds a plot with the title "Deaths from..."
dygraph(all, "Deaths from Lung Disease (UK)") %>%
  
  # changes the "ldeaths" label" to "Actual"
  dySeries("ldeaths", label = "Actual") %>%
  
  # combines the three prediction lines into a single line
  # that is named "Predicted" and has a confidence band
  dySeries(c("p.lwr", "p.fit", "p.upr"), label = "Predicted") %>%
  
  # adds a range selector beneath the graph
  dyRangeSelector()
```

***

```{r echo=FALSE, message=FALSE}
library(reportsWS)
library(forecast)

# Select name and gender
name <- "Gillian"    # Always capitalize
sex <- "F"           # or "M"
names <- get_babyname(name, sex)

# Create time series and forecast
nbirths <- ts(names$n, start = 1880)
mod <- auto.arima(nbirths)
pred <- forecast(mod, h = 12) # 12 for 2025
```

Since 1880, `r sum(nbirths, na.rm = TRUE)` children have been named **`r name`**. The graph below breaks this number down by year showing the number of children named `r name` as a time series. 

```{r echo = FALSE, warning = FALSE}
# Make plot
title <- paste0("Number of children named ", name)
all <- bind_as_xts(nbirths, pred) 
plot(all, main = title)
```

We modeled this time series with an `r trim_whitespace(pred$method)` model to predict the number of children that will be given the name `r name` in 2025.

```{r echo = FALSE}
knitr::kable(data.frame(
  method = trim_whitespace(pred$method), 
  predicted_2025 = round(xts::last(pred$mean))), "markdown")
```

