---
title: "What's in a name?"
author: "Garrett Grolemund"
date: "February 24, 2015"
output: html_document
runtime: shiny
---

```{r}
# Exercise 4: Use components of this interactive document to recreate the Shiny wep app in the slides. To do this, you will need to 
# 1. Open a new file and save it as `app.R`. In the file,
# 2. define a server object 
#    a. add the minimum necessary code for a server object
#    b. describe how to create the reactive expressions and 
#       rendered text that your app will need from the inputs 
#       that your app has.
#    c. save the rendered output in a way that you can access 
#       from the ui object
# 3. define a ui object
#    a. use Shiny functions to layout the app as it appears 
#       in the slides
#       i. for this app, use a navbarPage() with two tabPanel()s
#       ii. every column() must be in a fluidRow()
#    b. place the app's input widgets into the layout
#    c. place the app's rendered output into the layout
# 4. call shinyApp() at the very end of the file
```


```{r echo=FALSE, message=FALSE}
library(reportsWS)
library(forecast)
library(dygraphs)
library(shiny)

# Select name and gender
textInput(inputId = "name", label = "Type a name", value = "Garrett")
radioButtons(inputId = "sex", label = "Choose gender",
             choices = c("M", "F"), inline = TRUE)
names <- reactive(get_babyname(input$name, input$sex))

# Create time series and forecast
nbirths <- reactive(ts(names()$n, start = 1880))

pred <- reactive({
  mod <- auto.arima(nbirths())
  forecast(mod, h = 12) # 12 for 2025
})
```

Since 1880, `r renderText(sum(nbirths(), na.rm = TRUE))` children have been named **`r renderText(input$name)`**. The graph below breaks this number down by year showing the number of children named `r renderText(input$name)` as a time series. 

```{r echo = FALSE}
renderDygraph({
  title <- paste0("Number of children named ", input$name)
  all <- bind_as_xts(nbirths(), pred()) 

  dygraph(all, main = title) %>%
    dySeries("x", label = "n children") %>% 
    dySeries(c("lower", "fitted", "upper"), label = "Predicted") %>% 
    dyRangeSelector()
})
```

We modeled this time series with an `r renderText(trim_whitespace(pred()$method))` model to predict the number of children that will be given the name `r renderText(input$name)` in 2025.

```{r echo = FALSE}
renderTable({
  data.frame(
    method = trim_whitespace(pred()$method), 
    predicted_2025 = round(xts::last(pred()$mean)))
})
```

