---
title: "What's in a name?"
author: "Your name"
date: "Today's date"
output: html_document
---

The code chunk below uses the dygraphs library to plot an interactive chart of `ldeaths`, a data set in the dygraphs library.

Use the code as a model to replace the plot in our report at the bootom of the page with an interactive dygraph.

Note that the example code below is keyed to use the variable names `ldeaths`, `p.lwr`, `p.fit` and `p.upr`, which appear in the `all` object that the code creates.

_Your_ code should be keyed to use the variable names that appear in _your_ all object: `x`, `lower`, `fitted`, and `upper`.

```{r}
# loads dygraph library
library(dygraphs)

# preprocesses data (ignore this part:
# we've already preprocessed our data in the report below)
hw <- HoltWinters(ldeaths)
p <- predict(hw, n.ahead = 36, prediction.interval = TRUE)
all <- cbind(ldeaths, p)

# builds a plot with the title "Deaths from..."
dygraph(all, "Deaths from Lung Disease (UK)") %>%
  
  # changes the "ldeaths" label" to "Actual"
  dySeries("ldeaths", label = "Actual") %>%
  
  # combines the three prediction lines into a single line
  # that is named "Predicted" and has a confidence band
  dySeries(c("p.lwr", "p.fit", "p.upr"), label = "Predicted") %>%
  
  # adds a range selector beneath the graph
  dyRangeSelector()
```

***

```{r echo=FALSE, message=FALSE}
library(reportsWS)
library(forecast)

# Select name and gender
name <- "Gillian"    # Always capitalize
sex <- "F"           # or "M"
names <- get_babyname(name, sex)

# Create time series and forecast
nbirths <- ts(names$n, start = 1880)
mod <- auto.arima(nbirths)
pred <- forecast(mod, h = 12) # 12 for 2025
```

Since 1880, `r sum(nbirths, na.rm = TRUE)` children have been named **`r name`**. The graph below breaks this number down by year showing the number of children named `r name` as a time series. 

```{r echo = FALSE, warning = FALSE}
# Make plot
title <- paste0("Number of children named ", name)
all <- bind_as_xts(nbirths, pred) 
plot(all, main = title)
```

We modeled this time series with an `r trim_whitespace(pred$method)` model to predict the number of children that will be given the name `r name` in 2025.

```{r echo = FALSE}
knitr::kable(data.frame(
  method = trim_whitespace(pred$method), 
  predicted_2025 = round(xts::last(pred$mean))), "markdown")
```

