---
title: "Exercise 9 - Delay reactions"
output: html_document
runtime: shiny
---

`isolate()` provides a useful way to delay reactions when combined with an `actionButton()`. To see this:

1. Remove `eval = FALSE` from the code chunk below.

2. Use `isolate()` to prevent the histogram from updating when the selectbox changes. 
    + In general, it is a good idea to wrap as little code in `isolate()` as possible, even if you have to call `isolate()` twice. Check that your method worked.

3. Add an `actionButton()` like `actionButton("go", "Go!")` to your document. Place it before the call to `renderPlot()`. 

4. Call the action button from within `renderPlot()`. Then `renderPlot()` will reupdate whenever the action button changes (e.g. is clicked). 
    + `renderPlot()` does not need to do anything particular with the button's value, it can just look it up and then move on to the histogram.

5. Re-render the document. Change the select box. What happens to the plot? Click the action button. What happens to the plot?

```{r echo=FALSE}
selectInput("iriscol", label = "Select a variable", choices = names(iris))
```


```{r echo=FALSE}
renderPlot({
  # call the action button here
  hist(iris[[input$iriscol]], probability = TRUE, 
       xlab = input$iriscol)
})
```
