---
title: "What's in a name?"
output: html_document
---

Turn this file into an interactive document with Shiny components. To do this:

1. Prepare the document to run shiny and call shiny functions
2. Add an input function to collect a name value
3. Add an input function to collect a sex value
    + The value choices _must_ be `"M"` and `"F"`
4. Correctly call each R object in the file so that it reacts when the user changes an input value.
    + consider how to refer to the object (`name` v. `input$name` v. `names()`)
    + consider how to treat the object
        + do you need to wrap the code that calls it in one of 
            + `reactive()`
            + `render*()`
            + `observeEvent()`
            + `eventReactive()`
        + does that change how you need to refer to the output of the code?
5. Use `renderDygraph` from the dygraphs package to render your dygraph plot
6. Re-render the document frequently as you work to catch errors early.
    + to make this easy, I've commented out each R object. Errors will come only from the objects you have worked on (uncomment as you go).

***

```{r echo=FALSE, message=FALSE}
library(reportsWS)
library(forecast)
library(dygraphs)

# SELECT A NAME
# SELECT A SEX ("M" or "F")

# names <- get_babyname(name, sex)

# Create time series and forecast
#nbirths <- ts(#names$n, start = 1880)
#mod <- auto.arima(#nbirths)
#pred <- forecast(#mod, h = 12) # 12 for 2025
```

Since 1880, `r #sum(#nbirths, na.rm = TRUE)` children have been named **`r #name`**. The graph below breaks this number down by year showing the number of children named `r #name` as a time series. 

```{r echo = FALSE, fig.width = 6}
# title <- paste0("Number of children named ", #name)
# all <- bind_as_xts(#nbirths, #pred) 

# dygraph(all, main = title) %>%
#   dySeries("x", label = "n children") %>% 
#   dySeries(c("lower", "fitted", "upper"), label = "Predicted") %>% 
#   dyRangeSelector()
```

We modeled this time series with an `r #trim_whitespace(#pred$method)` model to predict the number of children that will be given the name `r #name` in 2025.

```{r echo = FALSE}
# data.frame(
#   method = trim_whitespace(#pred$method), 
#   predicted_2025 = round(xts::last(#pred$mean)))
```
