---
title: "Exercise 9 - Delay reactions"
output: html_document
runtime: shiny
---

`eventReactive()` provides a useful way to delay reactions when combined with an `actionButton()`. To see this:

1. Remove `eval = FALSE` from the code chunk below.

2. Add an `actionButton()` like `actionButton("go", "Go!")` to your document. Place it before the call to `renderPlot()`. 

3. Monitor the action button with `eventreactive()`. Arrange for `eventreactive()` to create a reactive expression that updates whenever the button is pressed. The expression should contain the results of `iris[[input$iriscol]]`. 

4. Remove `iris[[input$iriscol]]` from the call to `renderPlot()`. Have `renderPlot()` call the reactive expression above in its place.

5. Re-render the document. Change the select box. What happens to the plot? Click the action button. What happens to the plot?

```{r echo=FALSE}
selectInput("iriscol", label = "Select a variable", choices = names(iris))
```


```{r echo=FALSE}
renderPlot({
  # call the action button here
  hist(iris[[input$iriscol]], probability = TRUE)
})
```
