---
title: "Solution 3 - Knitr chunk options"
output: html_document
---

For each knitr code chunk option below

1. Add the option to the code chunk it accompanies.
2. Rerender the file to see what the option does. If you cannot tell, rerender the file both with and without the code chunk.
3. Describe in your own words what the option does.

***

`eval = FALSE` 

```{r eval = FALSE}
colMeans(cars)
```
Description: `eval = FALSE` does not run the code. As a result, it does not display the results.

***

`results = 'hide'` 

```{r}
carmeans <- colMeans(cars)
```

```{r}
# Hint: this code would give an error if you 
# added `eval = FALSE` to the chunk above
carmeans
```
Description: `results = 'hide'` runs the code, but does not display the results. This is convenient if you would like to use the results later in a new code chunk.

***

`echo = FALSE`

```{r}
plot(cars)
```
Description: `echo = FALSE` hides the code in the chunk, but displays the results of the code.

***

`fig.width = 5, fig.height = 4`  
When adding multiple arguments to a code chunk, separate the arguments by a comma.

```{r}
plot(cars)
```
Description: `fig.width = 5, fig.height = 4`  resize any figures made by the chunk to be 5 _inches_ by 4 _inches_.

***

`message = FALSE`   

```{r}
# libraries like to print messages
library(forecast)
```
Description: `message = FALSE` hides any messages generated by the chunk. (When `message = TRUE`, the default, messages will be added to the report.) 

***

`warning = FALSE`
```{r}
warning("This function returns a warning!")
```
Description: `message = FALSE` hides any warnings generated by the chunk. (When `message = TRUE`, the default, warnings will be added to the report.) 
***